CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-12-14 codecheck-paper.tex
fix label and URLs as footnotes

\section*{Implementation}\label{register}

@@

However, no approach besides CODECHECK spans across journals and is
intentionally designed to be picked up and implemented by many different 
journals or events, and to build a community of codecheckers. CODECHECK shares
this interdisciplinary nature with other community iniatives concered with 
reproducibility awareness, education, and supports, such as ReproHack
\footnote{\url{https://reprohack.github.io/reprohack-hq/}}, Code Copilot
\footnote{\url{https://twitter.com/Code_Copilot}}, or Papers with Code
\footenote{\url{https://paperswithcode.com/about}}.
The latter recently announced a collaborations with the preprint server
\emph{arXiv} on providing data and code supplements for machine learning
manuscripts\footnote{\url{https://medium.com/paperswithcode/papers-with-code-partners-with-arxiv-ecc362883167}} and runs a reproduciblity challenge
\footnote{\url{https://paperswithcode.com/rc2020}}.
% Papers with Code now also does more disciplines than just ML.
Likewise, different disciplines and journals provide reproducibility
checklists, e.g., \cite{rosenberg_next_2020}, which naturally share some
aspects while addressing particularities as well as addressing researchers
from different fields. Regarding the education and guidance for authors, 
we see CODECHECK's role in referencing and linking educational efforts
and helpful material, not as a creator and maintainer of content.

The journal \emph{ReScience C} publishes replications,
\url{https://rescience.github.io/faq/};
they do not accept proprietary software and require open source code;
they also required a third party to replicate; they also use Zenodo
to issue DOIs.
The journal \emph{Cortex} has a special article type 
\emph{Verification Reports}, which  actually are about replication of results 
but are very well designed/reasoned \cite{chambers_verification_2020}.
In a similar vein, the CODECHECK certificates
could also be published as a special article type within journals.

>>>>

\section*{Implementation}\label{implementation}

@@

However, no approach besides CODECHECK spans across journals and is
intentionally designed to be picked up and implemented by many different 
journals or events, and to build a community of codecheckers. CODECHECK shares
this interdisciplinary nature with other community iniatives concered with 
reproducibility awareness, education, and supports, such as ReproHack
\footnote{\url{https://reprohack.github.io/reprohack-hq/}}, Code Copilot
\footnote{\url{https://twitter.com/Code_Copilot}}, or Papers with Code
\footnote{\url{https://paperswithcode.com/about}}.
The latter recently announced a collaborations with the preprint server
\emph{arXiv} on providing data and code supplements for machine learning
manuscripts\footnote{\url{https://medium.com/paperswithcode/papers-with-code-partners-with-arxiv-ecc362883167}} and runs a reproduciblity challenge
\footnote{\url{https://paperswithcode.com/rc2020}}.
% Papers with Code now also does more disciplines than just ML.
Likewise, different disciplines and journals provide reproducibility
checklists, e.g., \cite{rosenberg_next_2020}, which naturally share some
aspects while addressing particularities as well as addressing researchers
from different fields. Regarding the education and guidance for authors, 
we see CODECHECK's role in referencing and linking educational efforts
and helpful material, not as a creator and maintainer of content.

The journal \emph{ReScience C} publishes replications
\footnote{\url{https://rescience.github.io/faq/}};
they do not accept proprietary software and require open source code;
they also required a third party to replicate; they also use Zenodo
to issue DOIs.
The journal \emph{Cortex} has a special article type 
\emph{Verification Reports}, which  actually are about replication of results 
but are very well designed/reasoned \cite{chambers_verification_2020}.
In a similar vein, the CODECHECK certificates
could also be published as a special article type within journals.
